### 2020-04-21 6_related.tex
Rewrite related work microbenchmark paragraph per Brad Chamberlain's feedback.

Microbenchmarks can be easier to implement, but risk being
unrepresentative of real applications. PRK Stencil~\cite{PRK14}
contains 2 kernels (which combined fit in under 50 lines of C++)
and a halo exchange on a structured grid; an
evaluation~\cite{PRKRuntimes16} compares MPI variants, SHMEM, UPC,
Charm++, and Grappa. The NAS benchmark suite~\cite{NAS91, NAS95}
consists mostly of small kernels for dense array computations and has
implementations in OpenMP~\cite{NASOpenMP99}, MPI and
MPI+OpenMP~\cite{NASMPIOpenMP00}, and
Charm++~\cite{NASCharm96}. Neither PRK nor NAS achieve the breadth of
coverage, flexibility, or ease of implementation of Task Bench. We
believe the evidence for ease of implementation is clear; Task Bench
is implemented for more systems than all previous mini-apps and
microbenchmarks. Task Bench is also not a fixed set of benchmarks, and
makes it easy to generate new benchmarks.

>>>>

Microbenchmarks can be easier to implement, but do not solve the
asymptotic costs of implementation. PRK Stencil~\cite{PRK14} contains a
2D stencil and is evaluated on implementations in MPI, SHMEM, UPC,
Charm++, and Grappa~\cite{PRKRuntimes16}. The NAS benchmark
suite~\cite{NAS91, NAS95} consists mostly of small kernels for dense
or sparse matrix computations and has implementations in
OpenMP~\cite{NASOpenMP99}, MPI and MPI+OpenMP~\cite{NASMPIOpenMP00},
and Charm++~\cite{NASCharm96}. PRK requires $\mathcal{O}(n)$ effort to
implement (for $n$ systems) by virtue of being only a single
computational pattern, while NAS requires $\mathcal{O}(mn)$ overall
effort (for $m$ patterns and $n$ systems). In contrast, Task Bench
requires $\mathcal{O}(m+n)$ effort and is easily extended to cover new
systems or patterns with $\mathcal{O}(1)$ effort for each additional
system or pattern.
